Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-02 paper/paper.qmd
fixed model

- $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level  
- $\mu$: Overall mean  
- $\alpha_i$: Effect of the $i$-th drug (categorical with 4 levels)  
- $\beta_j$: Effect of the $j$-th dosage level (categorical with 2 levels)  
- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
- $\epsilon_{ijk} \sim N(0, \sigma^2)$ : Random error

@@

# References
(Ha, 2010) https://journals.lww.com/ejanaesthesiology/FullText/2010/02000/Amitriptyline_rather_than_lornoxicam_ameliorates.6.aspx

>>>>

- $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level  
- $\mu$: Overall mean  
- $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))  
- $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage) 
- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
- $\epsilon_{ijk} \sim N(0, \sigma^2)$ : Random error

@@

# References
